powerboats with `hyper2`

### 2025-03-02 inst/powerboat.Rmd
update to new-style ordertable class

```{r}
powerboat_table[powerboat_table==0] <- "DNS"
powerboat_table[20:21,8] <- 0  # above does not apply to points
powerboat_table
```

>>>>

```{r}
powerboat_table[powerboat_table==0] <- "DNS"
powerboat_table[20:21,8] <- 0  # above does not apply to points
powerboat_table <- ordertable(powerboat_table)
powerboat_table
```
